---
title: "Testing constrained optimisation in Hydromad"
author: "Willem Vervoort"
date: "`r Sys.Date()`"
output: 
    pdf_document:
      fig_width: 7
      fig_height: 6
      fig_caption: true
---
```{r setup, warning=F, message=F}
# root dir
knitr::opts_knit$set(root.dir = "C:/Users/rver4657/ownCloud/working/constrOpt_hydromad")
knitr::opts_chunk$set(echo = TRUE)
# LOAD REQUIRED PACKAGES 
library(tidyr)
library(xts)
library(zoo)
library(hydromad)
library(lattice)
```

# testing constrained optimisation in hydromad

The idea is to include a constraint on the normal optimisation objective function (such as NSE or RMSE). The constraint needs to be that the individual error (pointwise error) should not be $> \beta$, $\beta$ is a small number that will be optimised. In essence this is the same as a regularisation, but in this case we use the \beta as a constraint.

# Hydromad standard fit

Load the hydromad Cotter test data and fit GR4J using simple optimisation

```{r Cotterdata}
data(Cotter)

data.cal <- window(Cotter, start = "1990-01-01",
                   end = "1998-12-31")

# Define the model, important to define return_state=T
Cotter_mod <- hydromad(DATA=data.cal,
                   sma = "gr4j", routing = "gr4jrouting", 
                   x1 = c(100,1500), x2 = c(-30,20), x3 = c(5,500), 
                   x4 = c(0.5,10), etmult=c(0.01,0.5), 
                   return_state=TRUE)

# Fit traditional fit
# Using Optim algorithm for fitting
Cotter_fit<- fitByOptim(Cotter_mod,  
                     objective=~hmadstat("r.squared")(Q,X))
# Extract the coefficients and the summary
summary(Cotter_fit)
xyplot(Cotter_fit)
```


# A new objective function

Define a new objective function that includes the constraint, refit the Cotter test data, check against standard fit.

## defining the objective function

This might be the trickiest bit, as this requires introducing a parameter, but how do we calibrate on this. First do the simple solution, basically we can choose beta and look at the results

```{r defineObjective}
hydromad.stats("ConstObj" = function(Q, X, ..., DATA = DATA, model = model, beta = 0.1) {
  # define norm(e_i_obs - e_i_fitted)
  #browser()
  norm_error <- sum(sqrt((coredata(Q) - coredata(X))^2) - beta, na.rm=T)/length(coredata(Q))
  obj <- hmadstat("r.squared")(Q, X, ...) + norm_error
  return(obj)
    })
```

## Calibrating the model

```{r fitConstrOptim}
# Using Optim algorithm for fitting
Cotter_Cfit<- fitByOptim_C(Cotter_mod,  
                     objective=~hmadstat("ConstObj")(Q=Q,X=X,DATA=DATA,model=Cotter_mod,beta=0.01))
# Extract the coefficients and the summary
summary(Cotter_Cfit)
xyplot(Cotter_Cfit)
```

## second try, use log(dnorm(residuals))
```{r defineObjective2}
hydromad.stats("ConstObjL" = function(Q, X, ..., DATA = DATA, model = model, mu=0, sigma = 0.1) {
  # define norm(e_i_obs - e_i_fitted)
  #browser()
  R <- dnorm((coredata(Q) - coredata(X)),mu,sigma)
  obj <- hmadstat("r.squared")(Q, X, ...) + log(R)
  return(obj)
    })
```

```{r fitConstrOptimL}
# Using Optim algorithm for fitting
Cotter_Cfit<- fitByOptim_C(Cotter_mod,  
                     objective=~hmadstat("ConstObjL")(Q=Q,X=X,DATA=DATA,model=Cotter_mod,mu=0, sigma = 0.1))
# Extract the coefficients and the summary
summary(Cotter_Cfit)
xyplot(Cotter_Cfit)
```

# Compare against standard ConstrOptim() or nloptr?




